Clinical prediction with localized modeling using similarity-based cohorts: A scoping review

### 2023-08-17 docs/Manuscript/Manuscript.Rmd
add citation numbers to remaining figures + avoid googlesheets in manuscript

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(stringr)
googlesheets4::gs4_auth(email = "cornelioid@gmail.com")
Sys.sleep(10)
```

@@

```{r tab:synthesis, echo=FALSE, message=FALSE, warning=FALSE}
tab_synthesis <- readr::read_rds(here::here("tab/synthesis.rds"))
tab_synthesis |> 
  select(-Date) |> 
  # prevent numeric list columns from dominating the horizontal space
  mutate(across(
    c(-Citation, -Cases, -Features),
    ~ str_c(., "\\hspace{6em}")
  )) |> 
  knitr::kable(
    align = "lllllrr",
    caption = paste0(
      "\\label{tab:synthesis}",
      "Studies included in the method synthesis,",
      " arranged by the earliest the study is known to have been public."
    )
  )
```

@@

```{r tab:composite, echo=FALSE, message=FALSE, warning=FALSE}
googlesheets4::read_sheet(
  ss = "1xvDJwiLBoI2oz8fxHJ5MjNmiju_RAlK7RJv-wXe1DAs", sheet = 1L
) |>
  rename_with(snakecase::to_snake_case) |>
  filter(is.na(synthesis)) |> 
  # mutate(zotero_key = str_split(zotero_key, "; ")) |> 
  # tidyr::unnest(zotero_key) |> 
  transmute(
    # Citation = paste0("@", zotero_key),
    Citation = sapply(
      str_split(zotero_key, "; "),
      function(s) str_c("[", str_c("@", s, collapse = "; "), "]")
    ),
    Elements = str_remove_all(approach_type_s, "\\[|\\]"),
    Terminology = term_s#,
    # Outcomes = outcome
  ) |> 
  mutate(Elements = str_replace_all(Elements, ",", ";")) |> 
  left_join(select(tab_synthesis, Citation, Date), by = "Citation") |> 
  arrange(Date) |> 
  select(-Date) |> 
  mutate(across(
    everything(),
    # ~ str_replace_all(., "<U+001B>", "")
    textclean::replace_non_ascii
  )) |>
  # mutate(across(c(Citation), ~ str_c(., "\\hspace{6em}"))) |> 
  knitr::kable(
    align = "lllllrr",
    caption = paste0(
      "\\label{tab:composite}",
      "Methodological elements of studies included in the synthesis. "
    )
  )
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(dplyr)
library(stringr)
Sys.sleep(10)
```

@@

```{r tab:synthesis, echo=FALSE, message=FALSE, warning=FALSE}
tab_synthesis <- readr::read_rds(here::here("tab/synthesis.rds"))
tab_synthesis |> 
  select(Citation, Task, Aim, Source, Type, Cases, Features) |> 
  # prevent numeric list columns from dominating the horizontal space
  mutate(across(
    c(-Citation, -Cases, -Features),
    ~ str_c(., "\\hspace{6em}")
  )) |> 
  knitr::kable(
    align = "lllllrr",
    caption = paste0(
      "\\label{tab:synthesis}",
      "Studies included in the method synthesis,",
      " arranged by the earliest the study is known to have been public."
    )
  )
```

@@

```{r tab:composite, echo=FALSE, message=FALSE, warning=FALSE}
composite_studies <- read_rds(here::here("tab/composite.rds"))
composite_studies |> 
  transmute(
    # Citation = str_c("@", Citation),
    Citation = sapply(
      str_split(Citation, "; "),
      function(s) str_c("@", s, collapse = "; ")
    ),
    Elements = str_replace_all(Elements, ",", ";"),
    Terminology
  ) |> 
  mutate(across(
    everything(),
    # ~ str_replace_all(., "<U+001B>", "")
    textclean::replace_non_ascii
  )) |>
  # mutate(across(c(Citation), ~ str_c(., "\\hspace{6em}"))) |> 
  knitr::kable(
    align = "lllllrr",
    caption = paste0(
      "\\label{tab:composite}",
      "Methodological elements of studies included in the synthesis. "
    )
  )
```
